### 2021-06-25 letter/responseLetter.tex

\vspace{0.2cm}

\item Another point to improve is connected to the implications of the study. While the paper discusses in nice way the 
results achieved, it does not provide a clear view of how those results can be potentially useful for researchers 
working on Android sandboxes as well as what are the next steps that the research community should pursue to 
improve the detection of malware.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} You are right. To mitigate this issue, we created a new Section 5 (Implications), that present how our results can be useful for both researchers and practitioner.}

@@

\vspace{0.2cm}

\item Last but not least, the threats to validity section should be improved, by commenting on conclusion and construct validity.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for this observation. We reviewed the Section 6 (Threats) to detail better internal and external validity. Concerning construct validity, we also add it at this Section.}

@@

\vspace{0.2cm}

\item Introduction, para 3 is repeating para 2

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Paragraphs 2 and 3 have indeed similar content. We reviewed Section 1 (Introduction) and removed paragraph 3.}

@@

\vspace{0.2cm}

\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
analysis must often assume that additional behaviors are possible than actually would be.''
Please explain

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We explained better this sentence at introduction, paragraph 2. Thanks for raising this issue.}

@@

\vspace{0.2cm}

\item Google play - Google Play
* java - Java / android - Android
* ``Another approach to rooting''
What is rooting?

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Sorry about these typos. We corrected all of them. Thank one more time. With respect to ``rooting'': It's a process performed on Android devices like smartphones or tablets, which allows users of the Android mobile operating system, to execute privileged commands that are typically unavailable at its default configuration. The term comes from the fact that Android system is based on Linux, and this system has a (superuser), called root, which has access to administrative permissions as on Linux. We insert a footnote with a link that better explain this term at page 5.\newline
(https://en.wikipedia.org/wiki/Rooting(Android))
}

@@

\vspace{0.2cm}

\item What are sensitive behaviors? ``showed that DroidBot is able to trigger an amount of sensitive behaviors''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Sensitive behaviors at Android context occurs when an Android app functionality can result in accessing or leaking of users sensitive data. Example of sensitive behaviors: File accesses and network access. We improve the text with this definition at Section 2 (Background and related works), paragraph 7.}

@@

\vspace{0.2cm}

\item Please rephrase:
``From the same authors, another test generator tool for Android, described as Humanoid [23], is a DroidBot evolution and
presents a proposal that can generate humans like tests inputs, using deep learning.''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We rephrase the text at Section 2 (Background and related works) paragraph 7, to better explain Humanoid test generation tool.}

@@

\vspace{0.2cm}

\item Briefly explain the taint analysis
``Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We agree that taint analysis explanation was very briefly. We reviewed our Section 2 (Background and related works), to better explain taint analysis from paragraph 9. We explained better the concept of ``source'' and ``sink'', and present how the analysis identifies sensitive information leakage, detecting taint flow between “source” and “sink”. To improve understanding, we also present a simple Listing (Listing 1), that present a simple data leakage example through data flows. }

@@

\vspace{0.2cm}

\item Section 3.1, the help text is not adding much value

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for raising this point. The section 3.1 presented our Benchmark tool DroidXP. The tool description was important for the paper since it was helpful for our first study conduction. DroidXP helped us to easily integrate different test generation tools, and understand the effect of the static analysis component at each tool. It was useful for us and can be very useful for other researchers. We
reviewed the first paragraph of section 3.1 to clarify the importance of DroidXP for our study conduction.}

@@

\vspace{0.2cm}

\item Please rephrase: ``After that, we executed the analysis again, though disabling the DroidFax static analysis algorithm''

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We reviewed the Section 3 (Study Settings) in full and so, we better explain the methodology. With this update, we removed this sentence.}

@@

\vspace{0.2cm}

\item There are several other typos and grammatical errors.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Sorry about these typos and grammar. We revised all the text, and corrected several mistakes that went unnoticed.}

### 2021-06-25 results.tex
update result and setup session

  \item[Humanoid] showed the worst performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. This might suggest that test generation
    tools that try to simulate the human behavior, such as Humanoid, are less effective to build Android sand boxes, in comparison
    with techniques that rely on random testing (such as Monkey). In the first execution (Exec. (WS)),
    the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%). Humanoid was the most affected in the second
    execution (Exec. (WOS)), whose resulting sandbox presents a reduction of $51.79$\%  in the number of detected malwares.
    Since the \blls did not explore Humanoid,
    we do not have a baseline for comparison with the previous work.

@@

To start with, consider the malicious version of the app \texttt{com.andoop.flyracing}---which both DroidBot and
Humanoid sandboxes could detect in our analysis. 
In this particular case, the malicious version changes the Android Manifest file,
adding permissions to receive and send SMS messages
(Listing~\ref{lst:androidManifest}). Adding these permissions, a malicious app may get money
fraudulently by sending messages without user confirmation, for instance.
The pair \texttt{L:M} indicates
a code segment that appears in line \texttt{L} of the malign (\texttt{M})
version of an app.

@@

\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
      AndroidManifest file of the malicious version.
      \texttt{B} stands for
      the benign version, while \texttt{M} stands for the malign version.}, language=XML,
    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]

@@

>>>>

  \item[Humanoid] showed the worst performance, even though a previous work~\cite{DBLP:conf/kbse/LiY0C19} presented that it leads to
    the highest number of lines coverage in comparison to Monkey, DroidBot, and DroidMate. This might suggest that, since Humanoid learn how humans interact with apps, and use the learned model to guide test generation, at simulate environment, this method to generate test inputs are less effective to build Android sandbox, in comparison with techniques that rely on random testing (such as Monkey). In the first execution (Exec. (WS)),
    the resulting Humanoid sandbox identified $56$ malwares in our dataset ($58.33$\%). Humanoid was the most affected in the second
    execution (Exec. (WOS)), whose resulting sandbox presents a reduction of $51.79$\%  in the number of detected malwares.
    Since the \blls did not explore Humanoid,
    we do not have a baseline for comparison with the previous work.

    an automated GUI test
generator that is able to learn how humans interact with
mobile apps and then use the learned model to guide test
generation as a human tester.

@@

To start with, consider the malicious version of the app \texttt{com.andoop.flyracing}---which both DroidBot and
Humanoid sandboxes could detect in our analysis. 
In this particular case, the malicious version changes the Android Manifest file,
adding permissions to receive and send SMS messages
(Listing~\ref{lst:androidManifest}). Adding these permissions, a malicious app may get money
fraudulently by sending messages without user confirmation, for instance.
The pair \texttt{L:M} indicates
a code segment that appears in line \texttt{L} of the malicious (\texttt{M})
version of an app.

@@

\begin{lstlisting}[caption={Diff in the file \texttt{com.andoop.flyracing}
      AndroidManifest file of the malicious version.
      \texttt{B} stands for
      the benign version, while \texttt{M} stands for the malicious version.}, language=XML,
    basicstyle=\fontsize{8}{6}\selectfont\ttfamily,label={lst:app65b}]

@@

\pgfplotsset{compat=1.9}% supress warning
\begin{filecontents*}{result.csv}
   App,Detected,Benign Source-Sinks,Malicious Source-Sinks,Execution Time (s)

\end{filecontents*}

%\begin{table}[ht]
%    \centering
%    \begin{tiny}
%        \begin{tabular}{c|c|c|c|c}%
%            \bfseries Pair App & \bfseries Detected & %\bfseries Source-sink (Benign) & \bfseries Source-sink %(Malicious) & \bfseries Execution Time (s)% specify %table head
%            \csvreader[head to column %names]{result.csv}{}% use head of csv as column names
%            {\\\hline\csvcoli&\csvcolii&\csvcoliii&\csvc%oliv&\csvcolv}% specify your coloumns here
%        \end{tabular}
%     \end{tiny}
%        \caption{Malwares detected in 96 pair (B/M) by %the taint analysis approach}
%        \label{tab:taintDetec}
%\end{table}

### 2021-06-25 setup.tex
update result and setup session

\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis. a.k.a effect of taint analysis on sandboxes. But in the introduction we kind of use the general S-D interaction and this problem interchangeably. I have left a comment at the introduction.}
Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of five {\bf dynamic analysis tools} (DroidMate, DroidBot, PUMA,
GUIRipper, and Monkey) for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured---in terms of malware
identification. 
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

We executed DroidXP using two
configurations. In the first (named WOS), we executed DroidXP
using the dataset of 96 pairs of Android apps---each pair
including a benign and a malign version,
the four test case generation tools (DroidBot, DroidMate, Monkey, and Humanoid),
and the \texttt{--disable-static-analysis} option of
DroidFax, which disables the
execution of the DroidFax static analysis
component from the experiment. The WOS configuration
runs the test case generation tools for three times, using
a time limit of three minutes. 
In the second configuration (named WS), we executed DroidXP
using the same dataset of 96 pairs of Android apps, though 
executing only a fake test case generator tool (named Joker)
{\bf without} the \texttt{--disable-static-analysis} option.
Joker simulates a test tool that does not
run the Android apps during an experiment execution.

>>>>

\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis. a.k.a effect of taint analysis on sandboxes. But in the introduction we kind of use the general S-D interaction and this problem interchangeably. I have left a comment at the introduction.}
Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of five {\bf dynamic analysis tools} (DroidMate, DroidBot, PUMA,
GUIRipper, and Monkey) for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured---in terms of malware
identification. 
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

We executed DroidXP using two
configurations. In the first (named WOS), we executed DroidXP
using the dataset of 96 pairs of Android apps---each pair
including a benign and a malign version,
the four test case generation tools (DroidBot, DroidMate, Monkey, and Humanoid),
and the \texttt{--disable-static-analysis} option of
DroidFax, which disables the
execution of the DroidFax static analysis
component from the experiment. The WOS configuration
runs the test case generation tools for three times, using
a time limit of three minutes. 
In the second configuration (named WS), we executed DroidXP
using the same dataset of 96 pairs of Android apps, though 
executing only a fake test case generator tool (named Joker)
{\bf without} the \texttt{--disable-static-analysis} option.
Joker simulates a test tool that does not
run the Android apps during an experiment execution, and your use revealed the performance of static analysis component of DroidFax.
